The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population

### 2023-02-21 Outputs/Paper/paper.qmd
Added section in quarto

### Bullying search droped after COVID-19

@@

### Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population

@@

@fig-5 shows the bullying searches in states with the bottom 10 Asian population. In all three metrics, there is a decrease in bullying searches in comparison to bullying searches in the top 10 states. The data shows that having a high population of Asian people did have an effect on school bullying searches during the pandemic. The higher the Asian population, the more bullying searches there were.

However, one weakness of this comparison is that there is sampling bias with this set. The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states. So naturally, there would be less bullying searches in a state like Montana, which has around 2.7% of California's total population. This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.

@@

# Discussion
## Bullying search relate to COVID-19

write a little here

@@

## Comparing top 10 with highest Asian population and bottom 10 states with lowest Asian population
write a little here

@@

>>>>

### Bullying search dropped after COVID-19

@@

### Comparing the Top 10 Asian Population states with the Bottom 10

@@

@fig-5, @fig-6, and @fig-7 shows the bullying searches in states with the 10 lowest percentage of Asian population. In all three metrics, there is a decrease in bullying searches in comparison to bullying searches in the top 10 states. The data shows that having a high population of Asian people did have an effect on school bullying searches during the pandemic. The higher the Asian population, the more bullying searches there were.

@@

# Discussion

@@

## Comparing the Top 10 Asian Population states with the Bottom 10
The top 10 Asian population states experienced more school and cyber bullying than the bottom 10 Asian population states. From (@cit7), there has been a 70% increase in Asian American cyberbullying in 2020. Anti-Asian xenophobia fueled by Covid-19 has led to an increase of hate towards Asian-Americans. With this in mind, Asian population does make an effect with respect to the disparity between bullying searches from the top 10 Asian population states with bullying searches from the bottom 10 Asian population states.

@@

In @fig-5, @fig-6, and @fig-7, there is sampling bias with these datasets. The total population numbers for the bottom 10 Asian population states are dwarfed by the total population numbers of the top 10 Asian population states. So naturally, there would be less bullying searches in a state like Montana, which has around 2.7% of California's total population. This is where our approach of using raw search data reaches it's limit, as we cannot draw an accurate comparison of search ratios due to the massive difference in total population numbers.
